Meta-analysis

### 2019-08-07 05_MetaAnalysis.Rmd
Change lmer analysis to predict errors to include all trials with standard deviation data Delete random slope imputing chunk

When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole. Sulphur was disregarded due to it's inconsistancy in efficacy.

@@

### standardising the type of variance

@@

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == "lsd (P=0.05)")%>%
   select(Trial_ref)%>%
   distinct()

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == "stdev")%>%
   select(Trial_ref)%>%
   distinct()

@@

```{r na2Sampling_variance}

@@

# method as described by Emerson
levels(factor(PM_MB_means$Y_error.type))

PM_MB_train <- PM_MB_means %>%
   filter(Y_error.type == "SamplingVariance")

@@

library(lme4)
library(scales)
# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER)

@@

@@

lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1,
               colour = c("Black",hue_pal()(6)))
   coord_cartesian(xlim = c(0.8, 1.2))

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))+
   coord_cartesian(xlim = c(0, 3))

@@

What is interesting about this model is the slopes all converge and pass through a specific point.
Perhaps can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.

```{r imputing_from_randomModel}
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))+
   coord_cartesian(xlim = c(2.85, 2.875), ylim = c(0.0048,0.0049))

# let us find the value of this point
# what are the slopes and intercepts for each random grouping factor (Trial_ref)
randomS_coefs <- lmer.coefx$Trial_ref

# lets write a funcion to generate a sequence of predicted Y (yield error) values
slope_generator <- function(slope,intercept, x_minimum = 0.8, x_maximum = 1.2, increment = 0.00000001){
   Xi <- seq(from = x_minimum, to = x_maximum, by = increment)
   (Xi * slope) + intercept
}

# generate a vector of predicted values for each of the trial slopes, returned as a matrix
tmp2 <- apply(randomS_coefs,1,FUN = function(x) {
   slope_generator(slope = x[1], intercept = x[2],x_minimum = 2.86135, x_maximum = 2.8614)
                      })
head(tmp2)

# find which X predictor gives the lowest variation between trials and therefore the closest to the point at which the slopes converge
tmp3 <- apply(tmp2,1,sd)
plot(tmp3)
min(tmp3)
x_3252 <- which(tmp3 == min(tmp3))

# zooming in on the X predictor by increasing resolution
seq(from = 2.85,to = 2.875, by =0.0001)[115]
seq(from = 2.85,to = 2.875, by =0.00001)[1139]
x_point <- seq(from = 2.86135,to = 2.8614, by =0.00000001)[x_3252]

# predict the y (yeild error) at the x predictor (grain.yield) for each trial group
tmp4 <- apply(randomS_coefs,1,FUN = function(x){
   (x_point * x[1]) + x[2]
})

# they are all the same value but lets take the mean to be more precise
y_point <- mean(tmp4)

# here is my 'good-enough' prediction of the convergence point
common_S_coordinate <- c(x_point, y_point)

```
After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope. Even though we know the grain yields and the mean in the grain yeilds we still can't predict the effect of the random intercept trial on the yield error.  
I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.

>>>>

## Investigating data and the number of factors represented in each Trial

### Fungicides
When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole. Sulphur was disregarded due to it's inconsistancy in efficacy.

@@

## Standardising the type of variance

@@

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(
      #Fungicide == "Tebeconazole",
       #   row_spacing == 0.75,
          Y_error.type == "lsd (P=0.05)")%>%
   select(Trial_ref)%>%
   distinct()

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(
         #Fungicide == "Tebeconazole",
         #row_spacing == 0.75,
          Y_error.type == "stdev")%>%
   select(Trial_ref)%>%
   distinct()

@@

```{r na2Sampling_variance}
library(lme4)
library(scales)

@@

# method as described by Emerson
PM_MB_train <- PM_MB_means %>%
   filter(Y_error.type == "SamplingVariance")

@@

# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER)

@@

# Lets try with Fungicide as a fixed effect
PM_MB_trianLMER.4 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ as.factor(Fungicide) + 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.4)
anova(PM_MB_trianLMER, PM_MB_trianLMER.4) # no significant difference between the models

@@

lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
dim(lmer.coef$Trial_ref)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1,
               colour = c("Black",hue_pal()(11)))+
   coord_cartesian(xlim = c(0, 3))

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1,
               colour = hue_pal()(11))+
   coord_cartesian(xlim = c(0, 3),
                   ylim = c(0, 1))

@@

After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope. Even though we know the grain yields and the mean in the grain yeilds we still can't predict the effect of the random intercept trial on the yield error.  
I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.
